\section{Introduction}

Event structures is a mathematical formalism introduced 
by Winskel~\cite{Winskel:86} as a semantic domain of concurrent programs.
In recent years there has been renewed interest in event structures, 
with the applications of the theory ranging from relaxed memory models%
~\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19}
to model-based mutation testing~\cite{Fellner-al:VMCAI2020}.
% \eupp{perhaps, we could add more citations once the related work is ready.}

The main advantage of event structures
compared to traditional interleaving semantics 
is that they give a more compact and concise 
representation of programs' behaviours.
For example, consider the following code snippet
of a simple parallel program.

\input{fig/intro-prog.tex}

\input{fig/intro-traces.tex}

Under the interleaving semantics,
it has $3! = 6$ traces with each trace consisting of $4$ events,
as depicted in \cref{fig:intro-traces}.
Events themselves represent atomic side-effects produced by instruction executions.
In our case, an event is either a \emph{write} of a value $a$ to a shared variable $x$ denoted as $\wlab{x}{a}$,
or a \emph{read} of a value $a$ from a shared variable $x$ denoted as $\rlab{x}{a}$.  

The same information can be encoded in a single 
event structure containing $6$ events in total
(see \cref{fig:intro-es}). 
In the event structure, there are two types of edges 
between the events. The grey arrows $e_1 \arrowCA e_2$ 
represent the \emph{causality relation}, a 
partial order reflecting the causal relationship
between the atomic events of computation.
The red edges $e_1 \arrowCF e_2$ represent 
the \emph{conflict relation} which is 
a symmetric and irreflexive relation 
encoding mutually exclusive events.
Each particular trace can be extracted from the event structure
as a linearisation of some \emph{configuration}, 
that is a causally-closed and conflict-free subset of events,  
which additionally should satisfy the constraint 
that each read is preceded by a matching write. 

\input{fig/intro-es.tex}

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like \coq~\cite{Coq},
\agda~\cite{Agda}, 
\isabelle~\cite{Nipkow-al:Isabelle2002}, 
\arend~\cite{Arend}, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

We have chosen \coq as the proof assistant because it's a mature formal proof management tool
with a rich ecosystem of libraries, plugins, documentation, and
existing applications including the certification of properties of programming languages:
the verified C compiler CompCert~\cite{Leroy-Compcert-CACM:2006},
the Verified Software Toolchain~\cite{Appel-ESOP2011} for verification of C programs,
and the Iris framework~\cite{Jung-al:JFP2018} for concurrent separation logic,
to name a few.

Our end goal is to develop a \coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow researchers 
to utilise the theory of event structures 
for the needs of their domain.

In this work-in-progress report, we sketch 
the common design principles behind our library
and give a concrete example of its usage  
by developing a formal mechanised semantics of a simple 
register machine with shared memory.

Our library together with the examples of 
its usage is available online at \url{https://github.com/event-structures/event-struct}.  
